XSFACE Analyses

### 2018-01-11 analysis-main/main_analyses_bll.Rmd

ggplot(mss, aes(x = factor(age.grp), y = face, col = posture)) +
  geom_boxplot() +
  ylab("Proportion Face Detections") +
  xlab("Age (months)") +
  facet_grid(~orientation) +
  ylim(c(0,.2)) +
  theme_bw()
```
# Face area: descriptives, posture and orientation
## When detected, how much of the field of view did faces occupy? (% of screen)

@@

## Face size as a function of continous age

@@

## Face size by infant's posture

>>>>

ggplot(mss, aes(x = factor(age.grp), y = face, col = posture)) +
  geom_boxplot() +
  ylab("Proportion Face Detections") +
  xlab("Age (months)") +
  facet_grid(~orientation) +
  ylim(c(0,.2)) +
  theme_bw()
```

# Face area: descriptives, posture and orientation

When detected, how much of the field of view did faces occupy? (% of screen)

## Descriptves by age

@@

## Face Area as a function of continous age

@@

## Face Area by infant's posture
